|

### 2023-01-15 paper.Rmd
autogit

```{r full_run_realWorldSymReg_problems, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/full_run_realWorldSymReg_problems.csv"),
  caption="Overview - Real World Symbolic Regression Benchmark Problems"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
Table X summarizes the median best fitness achieved after running each algorithm for 10 runs using a population size of 500 individuals for 30 generations.^[P-Values are marked with asteriks (1,2,3) for ($\alpha$)-levels of $0.1$, $0.05$ and $0.01$].

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c"
 #caption = "Symbolic Regression Overview - Mean final Fitness"
) %>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")

@@

@@

Next I studied the size of solutions based on using a pre-training strategy. Plot X shows the median size of the best solutions aggregated of all benchmark problems for symbolic regression

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "l"
 #caption = "Symbolic Regression Overview - Mean final Fitness"
) %>% row_spec(0,bold=FALSE) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

>>>>

```{r full_run_realWorldSymReg_problems, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/full_run_realWorldSymReg_problems.csv"),
  caption="Overview - Real World Symbolic Regression Benchmark Problems"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
Table X summarizes the median best fitness achieved after running each algorithm for 10 runs using a population size of 500 individuals for 30 generations.^[P-Values are marked with asteriks (1,2,3) for ($\alpha$)-levels of $0.1$, $0.05$ and $0.01$]. The median best fitness over all 30 generations are visualized in figure X.

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c",
 caption = "Median Best Fitness - Symbolic Regression"
) %>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")

@@

![Median Best Fitness - Symbolic Regression](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_fitness_byGens.png){height=80%}

@@

Next I studied the size of solutions based on using a pre-training strategy. Figure X shows the median size of the best solutions aggregated of all benchmark problems for symbolic regression

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "l",
 caption = "Median Solution Size - Symbolic Regression"
) %>% row_spec(0,bold=FALSE) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

```
## Population Diversity

Another interesting metric to examine in EC based metaheuristics is the diversity of the current generations population. Since the individual solutions in DAE-GP are computer programs in the form ob parse trees, I selected the normalized Levenshtein edit distance as my primary metric for tracking population diversity. figure X shows how the median population diversity develops over the full number of generations for all benchmark problems.

![Median Population Diversity over Generations](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_levDistance_byGen.png){height=80%}

Testing for statistical differences in the underlying distributions yields the P-Values listed in table X.

```{r full_run_realWorldSymReg_popDiversity, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

# Create the data frame from csv
df <- read.csv(
  "/Users/rmn/github/master_thesis/data/summary_table_median_LevDistance.csv",
  sep=",",
  colClasses = c("character", "numeric", "numeric", "numeric", "character", "character")
)

for(i in 1:nrow(df)){
  if(df[i, "DAE.GP"] < df[i, "Pre.Trained_DAE.GP"]){
    df_bold[i, "DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "DAE.GP"],2)))
    df_bold[i, "Pre.Trained_DAE.GP"] <- as.character(round(df[i, "Pre.Trained_DAE.GP"],2))
    }
  else if (df[i, "DAE.GP"] > df[i, "Pre.Trained_DAE.GP"]) {
    df_bold[i, "Pre.Trained_DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "Pre.Trained_DAE.GP"],2)))
  df_bold[i, "DAE.GP"] <- as.character(round(df[i, "DAE.GP"],2))
  }
}
# shorten column names
col_names <- c("Problem", "Hid.Layers", "DAE-GP", "Pre-Trained", "P-Value", "Cliffs-Delta")

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c",
 caption = "Median Population Diversity over Generations - Symbolic Regression"
) %>% 
  kable_styling(latex_options = "scale_down", font_size = 7)

## Training epochs per Generation

One important argument for using pre-training is the reduction of runtime and computational ressources for DAE-GP. An important factor in this, is the number of epochs that each DAE-LSTM has to be trained per generation. I studied the median number of training epochs that each generations DAE-LSTM $M_g$ (excluding the pre-training DAE-LSTM model $\hat{M}$) was trained until the training was stopped. The results are visualized in figure X and summarized in table X

![Median Number of Training Epochs per Generation - Symbolic Regression](~/masterThesis/master_thesis/img/symbolicRegressionSummarized/median_epochsTrained.png){height=80%}

```{r full_run_realWorldSymReg_epochsPerGen, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

# Create the data frame from csv
df <- read.csv(
  "/Users/rmn/github/master_thesis/data/summary_table_mean_epochsTrained.csv",
  sep=",",
  colClasses = c("character", "numeric", "numeric", "numeric", "character", "character")
)

for(i in 1:nrow(df)){
  if(df[i, "DAE.GP"] < df[i, "Pre.Trained_DAE.GP"]){
    df_bold[i, "DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "DAE.GP"],2)))
    df_bold[i, "Pre.Trained_DAE.GP"] <- as.character(round(df[i, "Pre.Trained_DAE.GP"],2))
    }
  else if (df[i, "DAE.GP"] > df[i, "Pre.Trained_DAE.GP"]) {
    df_bold[i, "Pre.Trained_DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "Pre.Trained_DAE.GP"],2)))
  df_bold[i, "DAE.GP"] <- as.character(round(df[i, "DAE.GP"],2))
  }
}
# shorten column names
col_names <- c("Problem", "Hid.Layers", "DAE-GP", "Pre-Trained", "P-Value", "Cliffs-Delta")

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c",
 caption = "Median Number of Training Epochs per Generation - Symbolic Regression"
) %>% 
  kable_styling(latex_options = "scale_down", font_size = 7)
